---
title: Publication bias and outlier analyses
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
---

**Load packages and dataset**
```{r setup, echo = TRUE, message = FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	error = FALSE, 
	fig.width=8, 
	fig.height=6
)
windowsFonts(Times = windowsFont("Times New Roman"))
options(scipen = 999, digits = 2)


library(groundhog)
groundhog.library(c("tidyverse", "metafor", "meta"), date = "2024-02-14")
groundhog.library("github::MathiasHarrer/dmetar", date = "2024-02-14")

```



# Meta-analysis 1
```{r}
MA1 <- readRDS("data/preprocessed/MA_all.rds") %>% 
  filter(id_ma == 1)
```


## Publication bias analysis
The analysis in this section mostly follows the tutorial [here](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/pub-bias.html#addressing-pubbias).

### PET-PEESE
Collate the necessary variables
For the PET-PEESE model, the effect sizes (here SMDs), their SEs, their variances, and their inverse-variance weights, are needed.
```{r}
petpeese <- data.frame(smd = MA1$smd_ma) # smds
petpeese$v <- MA1$v_ma # sampling variances (extracted from the figures)
petpeese$se <- MA1$se_ma # standard errors of SMD estimates
petpeese$w <- 1/petpeese$v # inverse variance weights
```

PET (precision-effect test)
```{r}
pet <- lm(smd ~ se, weights = w, data = petpeese)
summary(pet)$coefficients
```

PEESE (precision-effect estimate with standard error)
```{r}
peese <- lm(smd ~ v, weights = w, data = petpeese)
summary(peese)$coefficients
```
Both estimates indicate the presence of publication bias.


### P-Curve

P-Curve
```{r}
ma3 <- metagen(TE = smd_ma,
              seTE = se_ma,
              studlab = as.character(id_comparison),
              data = MA1,
              sm = "SMD",
              fixed = FALSE,
              random = TRUE, # a random effects MA.
              method.tau = "DL", # DerSimonian-Laird estimator
                 )

pcurve(ma3, 
       effect.estimation = TRUE,
       N = MA1$nt_ma + MA1$nc_ma, 
       dmin = 0,
       dmax = 1)
```
No indication of bias.


### Three-parameter selection model
Create a `metafor` package meta-analysis object, necessary for the `selmodel` function
```{r}
ma3_metafor <- rma(yi = smd_ma,        
          sei = se_ma,
          data = MA1,
          method = "DL")
```

Fit the selection model
```{r}
selmodel(ma3_metafor,
         type = "stepfun",
         steps = 0.025)
```
No indication of bias.


## Outlier/influence diagnostics
### Leave-one-out analysis
```{r}
metainf(ma3, pooled = "random")
```
Removing SMD 8 for example would reduce the pooled SMD by ~ 0.05 and considerably reduce the variance.

### Some plots
Baujat 
```{r}
outl <- InfluenceAnalysis(ma3, random = TRUE, text.scale = 2)
plot(outl, "baujat", )
```

Forest plot
```{r}
outl <- InfluenceAnalysis(ma3, random = TRUE, text.scale = 1.5)
plot(outl, "ES", text.scale = 2)
```


SMDs 6, 7, and 8 contribute disproportionately to both the variance and the pooled SMD.

### Run meta-analysis without outliers
```{r}
s <- update(ma3, subset = -c(6, 7, 8))
forest(s,

            print.tau2 = TRUE,
            leftlabs = c("SMD No.", "d", "SE"))
```
Removing the outliers increases the pooled SMD by ~ 0.07 and eliminates between-study heterogeneity altogether.

# Meta-analysis 2
```{r}
MA2 <- readRDS("data/preprocessed/MA_all.rds") %>% 
  filter(id_ma == 2)
```

## Publication bias analysis

### PET-PEESE
Collate the necessary variables
For the PET-PEESE model, the effect sizes (here SMDs), their SEs, their variances, and their inverse-variance weights, are needed.
```{r}
petpeese <- data.frame(smd = MA2$smd_ma) # smds
petpeese$v <- MA2$se_ma^2 # sampling variances (extracted from the figures)
petpeese$se <- MA2$se_ma # standard errors of SMD estimates
petpeese$w <- 1/petpeese$v # inverse variance weights
```

PET (precision-effect test)
```{r}
pet <- lm(smd ~ se, weights = w, data = petpeese)
summary(pet)$coefficients
```

PEESE (precision-effect estimate with standard error)
```{r}
peese <- lm(smd ~ v, weights = w, data = petpeese)
summary(peese)$coefficients
```


### P-Curve

P-Curve
```{r}
ma3 <- metagen(TE = smd_ma,
              seTE = se_ma,
              studlab = as.character(id_comparison),
              data = MA2,
              sm = "SMD",
              fixed = FALSE,
              random = TRUE, # a random effects MA.
              method.tau = "DL", # DerSimonian-Laird estimator
                 )


pcurve(ma3, 
       effect.estimation = TRUE,
       N = MA2$nt_ma + MA2$nc_ma, 
       dmin = 0,
       dmax = 1)
```



### Three-parameter selection model
Create a `metafor` package meta-analysis object, necessary for the `selmodel` function
```{r}
ma3_metafor <- rma(yi = smd_ma,        
          sei = se_ma,
          data = MA2,
          method = "DL")
```

Fit the selection model
```{r}
selmodel(ma3_metafor,
         type = "stepfun",
         steps = 0.025)
```



## Outlier/influence diagnostics
### Leave-one-out analysis
```{r}
metainf(ma3, pooled = "random")
```


### Some plots
Baujat 
```{r}
outl <- InfluenceAnalysis(ma3, random = TRUE, text.scale = 2)
plot(outl, "baujat")
```

Forest plot
```{r}
outl <- InfluenceAnalysis(ma3, random = TRUE, text.scale = 1.5)
plot(outl, "ES", text.scale = 2)
```

### Run meta-analysis without outliers
```{r}
s <- update(ma3, subset = -c(8, 9, 11, 19))
forest(s,

            print.tau2 = TRUE,
            leftlabs = c("SMD No.", "d", "SE"))
```

# Meta-analysis 3

```{r}
MA3 <- readRDS("data/preprocessed/MA_all.rds") %>% 
  filter(id_ma == 3)
```


## Publication bias analysis

### PET-PEESE
Collate the necessary variables
For the PET-PEESE model, the effect sizes (here SMDs), their SEs, their variances, and their inverse-variance weights, are needed.
```{r}
petpeese <- data.frame(smd = MA3$smd_ma) # smds
petpeese$v <- MA3$v_ma # sampling variances (extracted from the figures)
petpeese$se <- MA3$se_ma # standard errors of SMD estimates
petpeese$w <- 1/petpeese$v # inverse variance weights
```

PET (precision-effect test)
```{r}
pet <- lm(smd ~ se, weights = w, data = petpeese)
summary(pet)$coefficients
```

PEESE (precision-effect estimate with standard error)
```{r}
peese <- lm(smd ~ v, weights = w, data = petpeese)
summary(peese)$coefficients
```


### P-Curve

P-Curve
```{r}
ma3 <- metagen(TE = smd_ma,
              seTE = se_ma,
              studlab = as.character(id_comparison),
              data = MA3,
              sm = "SMD",
              fixed = FALSE,
              random = TRUE, # a random effects MA.
              method.tau = "DL", # DerSimonian-Laird estimator
                 )

pcurve(ma3, 
       effect.estimation = TRUE,
       N = MA3$nt_ma + MA3$nc_ma, 
       dmin = 0,
       dmax = 1)
```



### Three-parameter selection model
Create a `metafor` package meta-analysis object, necessary for the `selmodel` function
```{r}
ma3_metafor <- rma(yi = smd_ma,        
          sei = se_ma,
          data = MA3,
          method = "DL")
```

Fit the selection model
```{r}
selmodel(ma3_metafor,
         type = "stepfun",
         steps = 0.025)
```



## Outlier/influence diagnostics
### Leave-one-out analysis
```{r}
metainf(ma3, pooled = "random")
```


### Some plots
Baujat 
```{r}
outl <- InfluenceAnalysis(ma3, random = TRUE, text.scale = 2)
plot(outl, "baujat")
```

Forest plot
```{r}
outl <- InfluenceAnalysis(ma3, random = TRUE, text.scale = 1.5)
plot(outl, "ES", text.scale = 2)
```

### Run meta-analysis without outliers
```{r}
s <- update(ma3, subset = -c(2))
forest(s,

            print.tau2 = TRUE,
            leftlabs = c("SMD No.", "g", "SE"))
```
